---
title: "QMER Development Plan"
output:
  html_document: default
  header-includes:
  - \usepackage{titling}
  - \pretitle{\begin{center} \includegraphics[width=2in,height=2in]{figures/Letterhead1.png}}
  - \posttitle{\end{center}}
  pdf_document: null
  word_document: default
---

```{r, echo=FALSE}
htmltools::img(src = knitr::image_uri("figures/Letterhead1.png"), 
               alt = 'logo', 
               style = 'position:absolute; top:0; left:0; padding:10px;')
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## QMER Development Plan 2019 - 2021:

1.	Phase 1: 2019-2020: Foundation Development
    a.	Learning Community 
        i.	Offer monthly research roundtables
        ii.	Outreach for new students/faculty
        iii.	Offer 2-3 free workshops; 1 core skills, 1 method 
        iv.	Collect pre-post data from participants on outcomes
        v.	Develop listserv & profile of participants
        vi.	Preliminary survey of effectiveness from staff
            1.	IRB for collection
    b.	Local Data Center
        i.	Apply for IGP grant w/Biggio to support server
        ii.	Collect available local data – ongoing
        iii.	Identify open source practices and policies
    c.	Theory, Measurement, and Methodology Forum
        i.	Establish outreach format – newsletter & website
        ii.	Outline research agenda
        iii.	Develop teams & tasks

2.	Phase 2: 2020-2021: Expansion and Outreach
    a.	Learning Community
        i.	Continue monthly research roundtables
        ii.	Outreach for new students/faculty
        iii.	Offer In-Depth workshop (1-2 Days), charge
            1.	Utilize data from Data Center for trainings
        iv.	Offer 2-3 Workshops w/materials covered
        v.	Develop data to begin initial, local publication on program
        vi.	Explore AAAS NOYCE Grant for further development w/preliminary evidence – use for Good to Great
    b.	Local Data Center
        i.	Continue data collection
        ii.	Establish annual survey for students/faculty to state educators
        iii.	Deploy usage policies & procedures
    c.	Theory, Measurement, and Methodology Forum
        i.	Begin research dissemination 
        ii.	Initial agenda results
        iii.	Identify targets for outreach – LEA, ALSDE, etc. 
        iv.	Identify other institutional partners (U of A, UAB, etc)
